


```{r}
library(tidyverse)
df <- read.csv('turnover.csv')
glimpse(df)
```

  

```{r}
# Check duplicate row
print(paste('Duplicate row:' ,sum(duplicated(df))))

# Delete duplicate roe
df <- df[!duplicated(df), ]
row.names(df) <- NULL
nrow(df)
```

```{r}

fil_df <- df %>%
  filter(event == 1)
  
gender_header_gender <- prop.table(xtabs(fil_df$event ~ fil_df$gender + fil_df$head_gender)) %>%
  as.data.frame() %>%
  dplyr::select(gender = fil_df.gender, header_gender = fil_df.head_gender, total = Freq) %>%
  arrange(desc(total))

gender_header_gender[,3]  = round(gender_header_gender[,3], 2)

gender_header_gender

```



#### gender vs coach

```{r}

gender_coach <- prop.table(xtabs(fil_df$event ~ fil_df$gender + fil_df$coach)) %>%
  as.data.frame() %>%
  dplyr::select(gender = fil_df.gender, coach = fil_df.coach, total = Freq) %>% 
  arrange(desc(total))
  

gender_coach[,3]  = round(gender_coach[,3], 2)

gender_coach 

# as you can see that f and coach_no has the most turnover rate. so we try to input gender:coach in our model.
# Comparing to total resignation
```



#### Building industry has the most turnover rate at 76% comparing to its own industry.

```{r}
ind_leave <- fil_df %>%
 count(industry) %>%
 dplyr::select(industry, leave = n)

ind_total <- df %>%
 count(industry) %>%
 dplyr::select(total = n)

options(repr.plot.width=10, repr.plot.height=5)
cbind(ind_leave, ind_total) %>%
 mutate(proportion = round(leave/total, 2)) %>%
 dplyr::select(industry, proportion) %>%
 arrange(desc(proportion)) %>%
 head(3) %>%
 ggplot(aes(x= reorder(industry, proportion) , y=proportion)) +
 geom_bar(stat="identity", fill='#009E73') + 
 geom_text(aes(label=proportion ), hjust=1.9, color="white", size=5.5) + 
 theme( text = element_text(size = 25)) + 
 labs(x = 'Industry', y = 'Proportion') +
 coord_flip()
 
```

    
#### Employees who transports by car and bus resign from company at 52% comparing to its own transportation type.


```{r}
way_leave <- fil_df %>%
 count(way) %>%
 dplyr::select(way, leave = n)

way_total <- df %>%
 count(way) %>%
 dplyr::select(total = n)

options(repr.plot.width=10, repr.plot.height=5)
cbind(way_leave, way_total) %>%
 mutate(proportion = round(leave/total, 2)) %>%
 dplyr::select(way, proportion) %>%
 arrange(desc(proportion)) %>%
 head(3) %>%
 ggplot(aes(x=reorder(way, proportion), y=proportion)) +
 geom_bar(stat="identity", fill='#009E73') + 
 geom_text(aes(label=proportion), hjust=1.9, color="white", size=5.5) + 
 theme( text = element_text(size = 25)) + 
 labs(x = 'Way', y = 'Proportion') +
 coord_flip()
```



#### 66% of employees who get the position by referal method leave the company.

```{r}
traffic_leave <- fil_df %>%
 count(traffic) %>%
 dplyr::select(traffic, leave = n)

traffic_total <- df %>%
 count(traffic) %>%
 dplyr::select(total = n)

options(repr.plot.width=10, repr.plot.height=5)
cbind(traffic_leave, traffic_total) %>%
 mutate(proportion = round(leave/total, 2)) %>%
 dplyr::select(traffic, proportion) %>%
 arrange(desc(proportion)) %>%
 head(3) %>%
 ggplot(aes(x=reorder(traffic, proportion), y=proportion)) +
 geom_bar(stat="identity", fill='#009E73') + 
 geom_text(aes(label=proportion), hjust=1.9, color="white", size=5.5) + 
 theme( text = element_text(size = 25)) + 
 labs(x = 'Traffic', y = 'Proportion') +
 coord_flip()
```



#### 100% employees who is specialized in teaching from the data set leave the company.

```{r}
profession_leave <- fil_df %>%
 count(profession) %>%
 dplyr::select(profession, leave = n)

profession_total <- df %>%
 count(profession) %>%
 dplyr::select(total = n)

options(repr.plot.width=10, repr.plot.height=5)
cbind(profession_leave, profession_total) %>%
 mutate(proportion = round(leave/total, 2)) %>%
 dplyr::select(profession, proportion) %>%
 arrange(desc(proportion)) %>%
 head(3) %>%
 ggplot(aes(x=reorder(profession, proportion), y=proportion), fig(5,49)) +
 geom_bar(stat="identity", fill='#009E73') + 
 geom_text(aes(label=proportion), hjust=1.9, color="white", size=5.5) + 
 theme( text = element_text(size = 25)) + 
 labs(x = 'Profession', y = 'Proportion') +
 coord_flip()
```


#### Male supervisor has a little effect from female supervisor to resignation.


```{r}
head_gender_leave <- fil_df %>%
 count(head_gender) %>%
 dplyr::select(head_gender, leave = n)

head_gender_total <- df %>%
 count(head_gender) %>%
 dplyr::select(total = n)

options(repr.plot.width=12, repr.plot.height=6)
cbind(head_gender_leave, head_gender_total) %>%
 mutate(proportion = round(leave/total*100, 2)) %>%
 dplyr::select(head_gender, proportion) %>%
 arrange(desc(proportion)) %>%
 head(3) %>%
  ggplot(aes(x = '', y= proportion, fill= head_gender)) +
  geom_col() +
  geom_text(aes(label = paste(proportion, '%')), 
            position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y") + 
  theme( text = element_text(size = 20),
         axis.text = element_blank(),
         axis.ticks = element_blank(),
         panel.grid  = element_blank(),
         axis.title.x = element_blank(),
         axis.title.y = element_blank())
```


#### Proportion of greywage of resignation


```{r}

library(ggplot2)

pie_chart <- df %>% 
  dplyr::select(event, greywage) %>%
  filter(event == 1) %>%
  count(greywage) %>%
  dplyr::select (greywage, total = n) %>%
  mutate(percent = round(total/sum(total) * 100, 2))
  
options(repr.plot.width=12, repr.plot.height=6)
ggplot(pie_chart, aes(x = '', y= percent, fill= greywage)) +
  geom_col() +
  geom_text(aes(label = paste(percent, '%')), 
            position = position_stack(vjust = 0.5),
            size=6,
            color = 'white') +
  coord_polar(theta = "y") +
  theme( text = element_text(size = 20),
         axis.text = element_blank(),
         axis.ticks = element_blank(),
         panel.grid  = element_blank(),
         axis.title.x = element_blank(),
         axis.title.y = element_blank())

```

#### White wage in Retail industry has the most turnover rate about 20%


```{r}
wage_df <- df %>%
            filter(event == 1)

prop.table (xtabs(wage_df$event ~ wage_df$greywage + wage_df$industry)) %>%
  as.data.frame() %>%
  arrange(desc(Freq)) %>%
  head(5)

```


# Age and Work Experience distribution


```{r}
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

filter_df <- df %>%
    filter(event == 1)

hist(filter_df$age, breaks = 100, col = cbPalette[4], main = "Age Distribution", border = F, xlab = "Age")

hist(filter_df$stag, breaks = 100, col = cbPalette[4], main = "Work Experience Distribution", border = F, xlab = "Work Experience")




```



# Goal1: Indicate factor that is associated with event

# Plot Sample logit vs features


```{r}

logitplot<-function(y, x,ncat=15,...)
{
  brksx<-unique(quantile(x,probs=(0:ncat)/ncat))
  nbrksx<-length(brksx)
  cutx<-cut(x,breaks=brksx,include.lowest=TRUE)
  yt<-table(data.frame(y,cutx))
  mx<-tapply(x,cutx,FUN=mean)
  logity<-log((yt[2,]+0.5)/(yt[1,]+0.5))
  plot(mx,logity,...)
}

#reduced_model <-  step(glm(event ~ stag + I(stag^2) + gender + age + I(age^2) + I(age^3) + industry + profession + traffic + coach + head_gender + greywage + way + extraversion + I(extraversion^2) + I(extraversion^3) + independ + selfcontrol + I(selfcontrol^2)+ anxiety + I(anxiety^2) + novator + gender:head_gender, family = binomial(link = 'logit'), data = df) ,direction= "backward")


par(mfrow=c(3,3))
logitplot(df$event,df$stag,xlab="stag",ylab="adjusted sample logit") # second order
logitplot(df$event,df$age,xlab="age",ylab="adjusted sample logit") # Third order
logitplot(df$event,df$extraversion,xlab="extraversion",ylab="adjusted sample logit") # Third order
logitplot(df$event,df$independ,xlab="independ",ylab="adjusted sample logit")
logitplot(df$event,df$selfcontrol,xlab="selfcontrol",ylab="adjusted sample logit") # second order
logitplot(df$event,df$anxiety,xlab="anxiety",ylab="adjusted sample logit") # second order
logitplot(df$event,df$novator,xlab="novator",ylab="adjusted sample logit")
```


# Create Reduced model from data set by using step (AIC)


```{r}
reduced_assoc_model <-  step(glm(event ~ stag + I(stag^2) + gender + age + I(age^2) + I(age^3) + industry + profession + traffic + coach + head_gender + greywage + way + extraversion + I(extraversion^2) + I(extraversion^3) + independ + selfcontrol + I(selfcontrol^2)+ anxiety + I(anxiety^2) + novator + gender:coach , family = binomial(link = 'logit'), data = df) ,direction= "backward")

```


# Add  missing main effect after using step


```{r}
reduced_assoc_model <- glm(event ~ stag + gender + age + I(age^2) + I(age^3) + industry + profession + traffic + head_gender + way, family = binomial(link = 'logit'), data = df)
summary(reduced_assoc_model)

```


    

# Create Full model from data set


```{r}
full_assoc_model = glm(event ~ stag + I(stag^2) + gender + age + I(age^2) + I(age^3) + industry + profession + traffic + coach + head_gender + greywage + way + extraversion + I(extraversion^2) + I(extraversion^3) + independ + selfcontrol + I(selfcontrol^2)+ anxiety + I(anxiety^2) + novator + gender:coach , family = binomial(link = 'logit'), data = df)

summary(full_assoc_model)


```



# Compare nested model


```{r}
LRT <- deviance(reduced_assoc_model) - deviance(full_assoc_model)
pchisq(LRT, df.residual(reduced_assoc_model) - df.residual(full_assoc_model), lower.tail = F)
```


#### H0: Reduced model
#### H1: Full model
#### P-Value: 0.942961760169536 > 0.05 (Not Significant)
#### Conclusion: We fail to reject H0. We choose reduced model.

# Test goodness of fit test by HL Test


```{r}
hosmerlem <-function (y, yhat, g = 10)
{
cutyhat <- cut(yhat, breaks = quantile(yhat, probs = seq(0,1, 1/g)), include.lowest = T)
obs <- xtabs(cbind(1 - y, y) ~ cutyhat)
expect <- xtabs(cbind(1 - yhat, yhat) ~ cutyhat)
chisq <- sum((obs - expect)^2/expect)
P <- 1 - pchisq(chisq, g - 2)
c("X^2" = chisq, Df = g - 2, "P(>Chi)" = P)
}

hosmerlem(df$event, reduced_assoc_model$fitted.values)
```


#### H0: Model fits data
#### H1: Model does not fit data
#### P-Value: 0.739632078353907 > 0.05 (Not Significant)
#### Conclusion: We fail to reject H0. The Model fits data.

# Check influential point


```{r}

plot(reduced_assoc_model, 4)
abline(h = qf(0.5, reduced_assoc_model$rank, nrow(df)-reduced_assoc_model$rank), col='blue') # Rule1
abline(h = 4/nrow(df), col='red') # Rule2

print(paste('Rule1 F(0.5, p+1, n-p-1):',qf(0.5, reduced_assoc_model$rank, nrow(df)-reduced_assoc_model$rank)))
print(paste('Rule2 4/n:',4/nrow(df)))



```


#### From Cook's distance, We use 50th percentile of F(46-1,1116-46+1 ) = 0.98. Thus, there is no an influential point in our data.

# Check multicolinearity with VIF


```{r}
str(df)
```


```{r}
library(usdm)
vif(df[,c(-2,-3,-5,-6,-7,-8,-9,-10, -11)])


```


#### For numerical variables, there are no multicolinearity because their VIF value are nearly 1. 


```{r}
summary(reduced_assoc_model)
```


# Interpret coefficient of logistic regression
#### exp{-2.889e-01(0-1)} = 1.334958226
#### Comparing a woman with a man of the same age, the estimated odds ratio is exp{-2.889e-01(0-1)} = 1.334958226. Thus, a woman’s odds were about 1.33 times the odds of turnover of a man of the same age.


# Predictive Performance

# Check AUC of ROC


```{r}
library(pROC);

y_pred_reduce <-predict(reduced_assoc_model , newdata=df, type="response")
predclass_reduce<-rep(0, nrow(df))
truth_reduce<-df$event

roc(truth_reduce, y_pred_reduce, percent=TRUE, plot=TRUE,print.auc=TRUE, auc.polygon=TRUE, xlim=c(100,0))
```


# Check ROC curve to get youden index


```{r}
# Use 0.5 as cutoff point

predclass_reduce<-rep(0, nrow(df))

# Use youden index as cutoff point
youden_index <- 0.68 + 0.79 - 1 #youden_index <- 0.47

#youden_index <- 0.68 + 0.65 - 1

predclass_reduce[y_pred_reduce>=youden_index]<-1
truth_reduce<-df$event
xtab_reduce <-table(truth_reduce, predclass_reduce)
xtab_reduce
```


        
# Calculate Accuracy, Sensitivity, Specificity

```{r}
accuracy <- (xtab_reduce[1,1] + xtab_reduce[2,2]) / sum(xtab_reduce)
sensitivity <- xtab_reduce[2,2]/ (xtab_reduce[2,2] + xtab_reduce[2,1])
specification <- xtab_reduce[1,1] / (xtab_reduce[1,1] + xtab_reduce[1,2])
false_positive_rate <- 1-specification
print(paste('Accuracy:', round(accuracy, 2))) 
print(paste('Sensitivity:', round(sensitivity, 2))) # ความแม่นของการตรวจว่า ลาออก
print(paste('Specification:', round(specification, 2))) # ความแม่นของการตรวจว่า ไม่ลาออก
print(paste('False positive rate:', round(false_positive_rate, 2))) # โอกาสผิดของการตรวจว่า ลาออก
```

  
